---
title: "Beamer Slide Element Templates"
output: 
  beamer_presentation:
header-includes: \usepackage{multicol}
---



```{r  setup, echo = FALSE, include = FALSE, results='hide', message = FALSE, warning = FALSE}
require(knitr)
require(ggplot2)
require(here)

knitr::opts_chunk$set(root.dir = here(), error = TRUE)
knitr::opts_knit$set(echo = TRUE, error = TRUE, root.dir = here())

source(here("data", "environment_vars.R"))
img_dir = file.path("slides", "slide_images")

dat = read.csv(here("data/cedar_creek_survey.csv"))
gg = ggplot(dat, aes(x = Total.Individuals, y = Distinct.Species.Count))


express2 = "{`r here(img_dir, \"iClicker_logo.png\")`}"
express3 = "`r here(img_dir, \"question_mark_green.png\")`"

```


# iClicker Answer List Code
```
\begin{enumerate}[A]
  \item Q1
  \item Q2
  \item Q3
  \item Q4
  \item Q5
\end{enumerate}
```

# iClicker Answer List

\begin{enumerate}[A]
\item Q1
\item Q2
\item Q3
\item Q4
\item Q5
\end{enumerate}


# iClicker Logo Code
```
\begin{multicols}{2}
\null \vfill
\vfill \null
\columnbreak
\includegraphics[width = 0.35\textwidth]{`r express2`}
\end{multicols}
```

# iClicker Logo

\begin{multicols}{2}
\null \vfill
\vfill \null
\columnbreak
\includegraphics[width = 0.35\textwidth]{`r here(img_dir, "iClicker_logo.png")`}
\end{multicols}


# Image File Code
```
\begin{center}
    \includegraphics[width = 0.88\textwidth]
        {`r express3`}
\end{center}
```

# Image File
\begin{center}
    \includegraphics[width = 0.88\textwidth]
        {`r here(img_dir, "question_mark_green.png")`}
\end{center}


# R Figure I

```{r r figure fixed aspect, echo = FALSE, fig.asp = 0.6, warning = FALSE}
gg +
  geom_point() +
  xlab("Count of Individuals") +
  ylab("Count of Distinct Species") +
  ggtitle("Cedar Creek Rarefaction: Preliminary Data Exploration") +
  theme(text = element_text(size = 22))
```

# R Figure II

```{r r figure set height and width, echo = FALSE, fig.width = 8, fig.height = 7, warning = FALSE}
gg +
  geom_point() +
  xlab("Count of Individuals") +
  ylab("Count of Distinct Species") +
  ggtitle("Cedar Creek Rarefaction: Preliminary Data Exploration") +
  theme(text = element_text(size = 22))
```


# Nested List

The data (i.e. the variables):

\begin{enumerate}
  \item Response Variable
  \begin{enumerate}
    \item the variable of interest
  \end{enumerate}
  \item Explanatory Variables
  \begin{enumerate}
    \item predictor
  \end{enumerate}
\end{enumerate}


# Nested List Code
```
\begin{enumerate}
  \item Response Variable
  \begin{enumerate}
    \item the variable of interest
  \end{enumerate}
  \item Explanatory Variables
  \begin{enumerate}
    \item predictor
  \end{enumerate}
\end{enumerate}

```



# Equations Code

```
\begin{equation}
   \label{eq:example-equation}
   y = mx + b
\end{equation}

\begin{equation}
   \label{eq:example-equation}
   y_{i} = 
   \alpha + 
   \beta_{1} \times 
   x_{i1} + 
   \beta_{2} \times 
   x_{i2} + 
   \epsilon
\end{equation}
```

# Equations

\begin{equation}
   \label{eq:example-equation}
   y = mx + b
\end{equation}

\begin{equation}
   \label{eq:example-equation}
   y_{i} = \alpha + \beta_{1} \times x_{i1} + \beta_{2} \times x_{i2} + \epsilon
\end{equation}



# Figure and Footnote Code

```
\begin{center}
    \includegraphics[width = 0.35\textwidth]
       `r express2`
\end{center}

\footnotetext[1]
   {Figure 4.3 in Fletcher and Fortin, 2018}
```

# Figure and Footnote

\begin{center}
\includegraphics[width = 0.35\textwidth]{`r here(img_dir, "iClicker_logo.png")`}
\end{center}

\footnotetext[1]{Figure 4.3 in Fletcher and Fortin, 2018}